Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-09-11 manuscript/draft.Rmd
Minor pre-submission changes
* Citations
* Don't promise non-existent appendix

All analyses were conducted using R [@R]. Primary R packages used in the
analysis included dplyr [@dplyr], tidyr [@tidyr], gimms [@gimms], sp [@sp1;
@sp2], raster [@raster], prism [@prism], rdataretriever [@rdataretriever],
forecast [@forecast1; @forecast2], git2r [@git2r], ggplot [@ggplot2], mistnet
[@harris2015], viridis [@viridis], rstan [@rstan], yaml [@yaml], purrr [@purrr],
gbm [Ridgeway *et al.* -@gbm], randomForest [@randomForest]. Code to fully
reproduce this analysis is available on GitHub
(https://github.com/weecology/bbs-forecasting) and archived on Zenodo
(https://doi.org/10.5281/zenodo.839581).

@@

Accounting for differences among observers generally improved measures of model
fit (Figure 7). Improvements primarily resulted from a small number of forecasts
where observer turnover caused a large shift in the reported richness values
(Appendix [[Figure Number]]). The naive baseline was less sensitive to these
shifts, because it largely ignored the richness values reported by observers
that had retired by the end of the training period (Figure 1). The average
model, which gave equal weight to observations from the whole training period,
showed a larger decline in performance when not accounting for observer effects
-- especially in terms of coverage. The performance of the mistnet JSDM was
notable here, because its prediction intervals retained good coverage even when
not correcting for observer differences, which we attribute to the JSDM's
ability to model this variation with its latent variables.

@@

The science of forecasting biodiversity remains in its infancy and it is
important to consider weaknesses in current forecasting methods in that context.
In the beginning, weather forecasts were also worse than simple baselines, but
these forecasts have continually improved throughout the history of the field
[@mcgill2012; @silver2012; @bauer2015]. One practice that lead to improvements
in weather forecasts was that large numbers of forecasts were made publicly,
allowing different approaches to be regularly assessed and refined [@mcgill2012;
@silver2012]. To facilitate this kind of improvement, it is important for
ecologists to start regularly making and evaluating real ecological forecasts,
even if they perform poorly, and to make these forecasts openly available for
assessment [@mcgill2012; @dietze2016]. These forecasts should include both
short-term predictions, which can be assessed quickly, and mid- to long-term
forecasts, which can help ecologists to assess long time-scale processes and
determine how far into the future we can successfully forecast [@dietze2016;
@tredennick2016]. We have openly archived forecasts from all six models through
the year 2050 [@zenodo], so that we and others can assess how well they perform.
We plan to evaluate these forecasts and report the results as each new year of
BBS data becomes available, and make iterative improvements to the forecasting
models in response to these assessments.

>>>>

All analyses were conducted using R [@R]. Primary R packages used in the
analysis included dplyr [@dplyr], tidyr [@tidyr], gimms [@gimms], sp [@sp1;
@sp2], raster [@raster], prism [@prism], rdataretriever [@rdataretriever],
forecast [@forecast1; @forecast2], git2r [@git2r], ggplot [@ggplot2], mistnet
[@harris2015], viridis [@viridis], rstan [@rstan], yaml [@yaml], purrr [@purrr],
gbm [Ridgeway *et al.* -@gbm], randomForest [@randomForest]. Code to fully
reproduce this analysis is available on GitHub
(https://github.com/weecology/bbs-forecasting) and archived on Zenodo
[@zenodoCode].

@@

Accounting for differences among observers generally improved measures of model
fit (Figure 7). Improvements primarily resulted from a small number of forecasts
where observer turnover caused a large shift in the reported richness values.
The naive baseline was less sensitive to these shifts, because it largely
ignored the richness values reported by observers that had retired by the end of
the training period (Figure 1). The average model, which gave equal weight to
observations from the whole training period, showed a larger decline in
performance when not accounting for observer effects -- especially in terms of
coverage. The performance of the mistnet JSDM was notable here, because its
prediction intervals retained good coverage even when not correcting for
observer differences, which we attribute to the JSDM's ability to model this
variation with its latent variables.

@@

The science of forecasting biodiversity remains in its infancy and it is
important to consider weaknesses in current forecasting methods in that context.
In the beginning, weather forecasts were also worse than simple baselines, but
these forecasts have continually improved throughout the history of the field
[@mcgill2012; @silver2012; @bauer2015]. One practice that lead to improvements
in weather forecasts was that large numbers of forecasts were made publicly,
allowing different approaches to be regularly assessed and refined [@mcgill2012;
@silver2012]. To facilitate this kind of improvement, it is important for
ecologists to start regularly making and evaluating real ecological forecasts,
even if they perform poorly, and to make these forecasts openly available for
assessment [@mcgill2012; @dietze2016]. These forecasts should include both
short-term predictions, which can be assessed quickly, and mid- to long-term
forecasts, which can help ecologists to assess long time-scale processes and
determine how far into the future we can successfully forecast [@dietze2016;
@tredennick2016]. We have openly archived forecasts from all six models through
the year 2050 [@zenodoPredict], so that we and others can assess how well they
perform. We plan to evaluate these forecasts and report the results as each new
year of BBS data becomes available, and make iterative improvements to the
forecasting models in response to these assessments.
